---
title: "R Markdown Test"
author: "Matthew Fritscher"
date: '2023-01-27'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Predicting Inflation/Unemployment

Background on federal funds rate and how it affects inflation/unemployment goes here...

## Loading in the dataset 

```{r}
df <- econ_data
summary(df)
```

Here we can see there are some columns that have a lot of missing values

I want to create a function that fills in the appropriate missing values for unemployment and inflation.
This function will find the 4 records before and 4 records after and take that average, and fill the missing value with this average.

```{r}

averager <- function (column_name){
  column_name <- as.list(column_name)
  return (summary(column_name))
}

averager(df[["Inflation Rate"]])


```





```{r}

fill_nas <- function(column_name){
  column_name <- as.list(column_name)
  for (x in column_name){
    if (x == is.na()){
      x <- 0
    }
    else{
      x <- x
    }
  }
}

```




```{r}
fill_nas(df[["Inflation Rate"]])
summary(df[["Inflation Rate"]])
```


